\large Multi-Robot Probabilistic Mapping and Exploration

### 2018-07-13 Dissertation/Defense/defense.tex
Acknowleged the NRL

\institute{\footnotesize
{\normalsize Evan Kaufman\\
\vspace*{0.2cm}
Dissertation Director: Taeyoung Lee}\\
\vspace*{0.3cm}
{\normalsize Committee Members:\\
 \vspace*{0.2cm}
Taeyoung Lee, James Hahn, Robert Pless,\\Chung-Hyuk Park, and Zhuming Ai}
\vspace*{0.4cm}\\
  Mechanical and Aerospace Engineering\\George Washington University
}

@@

\begin{frame}
\frametitle{Motivation}
\begin{itemize}
	\item Environments can be dangerous and uncertain
	\item Robots can replace humans for tasks such as surveillance, search-and-rescue, and cleaning
	\item Robot must understand their environment by generating a map, referred to as \emph{mapping}
	\item Selecting and performing robotic actions to maximize map information, referred to as \emph{autonomous exploration}, is necessary to optimally explore initially-uncertain environments
	\item Cooperative robots can share information to achieve a collective goal, referred to as \emph{multi-vehicle coordination}
	\item These task must be performed in 2D and 3D environments, where computational efficiency is paramount to real-time implementation
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{High-Level Contributions}
\begin{itemize}
	\item Occupancy Grid Mapping: solving the Bayesian solution to occupancy probability, known as the \emph{inverse sensor model}
	\pause
	\item Autonomous Exploration: novel approach to predicting future map uncertainty, known as \emph{Shannon's entropy}
	\pause
	\item Multi-Vehicle Coordination: \emph{bidding}-based framework for assigning tasks while exploring uncertain environments
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Outline}
\begin{itemize}
	\item Occupancy Grid Mapping
	\begin{itemize}
		\item Background and problem definition
		\item Common approaches and approximations
		\item Inverse sensor model in 1D
		\item Ray casting and measurement scans for 2D and 3D environments
		\item Numerical examples
	\end{itemize}
	\pause
	\item Autonomous Exploration
	\begin{itemize}
		\item Existing solutions: frontiers, expected measurements
		\item Proposed approach: entropy expectation
		\item Collision-free trajectories
		\item Optimal pose selection
		\item Numerical Examples
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Outline}
\begin{itemize}
	\item Multi-Vehicle Coordination
	\begin{itemize}
		\item Cooperative approaches
		\item Bidding-based framework
		\item Receding horizon
		\item Multi-vehicle autonomous exploration numerical example
		\item Autonomous patrol
		\item Multi-vehicle autonomous patrol numerical example
	\end{itemize}
	\pause
	\item Experiments
	\begin{itemize}
		\item Ground vehicle 2D mapping and autonomous exploration
		\item Flying quadrotor in large vertically-uniform space
		\item Flying quadrotor in complex 3D environment
	\end{itemize}
\end{itemize}
\end{frame}

@@

@@

\begin{frame}
\frametitle{Inexact Solutions}

@@

\begin{frame}
\frametitle{New Approach: Grouping}

@@

\begin{itemize}
	\item Unnormalized Probability:
	\begin{align*}
\tilde P(\mathbf{r}_{k}|z,X_{1:t},Z_{1:t-1})
&=\mathbf{P}_k^-
\bigg[\sum_{i=1}^{k-1}\bigg\{\prod_{j=0}^{i-1}\bar{\mathbf{P}}_j^-\bigg\}p(z|\mathbf{r}_{i+},X_t)\mathbf{P}_k^-\bigg]\nonumber\\
&\qquad + \bigg\{\prod_{j=0}^{k-1}\bar{\mathbf{P}}_j^-\bigg\}p(z|\mathbf{r}_{k+},X_t)\mathbf{P}_k^-
\end{align*}
	\item Normalizer:
	\begin{align*}
\label{eqn:allEta}
\eta
&=
\bigg[\sum_{i=1}^{n_{r}+1}\bigg\{\prod_{j=0}^{i-1}\bar{\mathbf{P}}_j^-\bigg\} p(z|\mathbf{r}_{i+},X_t)\mathbf{P}_k^-\bigg]^{-1}
\end{align*}
	\item Solution: $P(\mathbf{r}_{k}|z,X_{1:t},Z_{1:t-1})=\eta\tilde P(\mathbf{r}_{k}|z,X_{1:t},Z_{1:t-1})$
	\item \emph{Linear Complexity} ($\mathcal{O}(n)$ for \emph{all} $n$ cells in FOV)
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Full Measurement Scan}

\begin{itemize}
	\item Two Methods
	\begin{itemize}
		\item \emph{Ray-By-Ray Inverse Sensor Model}: each measurement ray is evaluated individually for updating the map
		\item \emph{Synergistic Scan Inverse Sensor Model}: all measurement rays are evaluated simultaneously
	\end{itemize}
\end{itemize}

\begin{frame}
\frametitle{Ray-By-Ray Inverse Sensor Model}

\begin{itemize}
	\item Main idea: given a scan of measurement rays, update the map based on each measurement ray \emph{individually} and \emph{sequentially}
	\item Conditional probability:
	\begin{align*}
		P(\mathbf{m}_i|X_{1:t}&,Z_{1:t})\nonumber\\&
		=P((\dots(((\mathbf{m}_i|X_{1:t},Z_{1:t-1})|z_{t,1})|z_{t,2})|\ldots)|z_{t,n_z})
	\end{align*}
	\item Benefit: the measurement rays maintain some dependency as they capture the same map
	\item Drawback: the best order for evaluating rays is not necessarily chosen
\end{itemize}

\begin{frame}
\frametitle{Synergistic Scan Inverse Sensor Model}

\begin{itemize}
	\item Main idea: consider every measurement ray inside a scan \emph{simultaneously} to update all grid cells inside the FOV
	\item Probability derived from a Bayesian approach:
	\begin{align*}
		P(\mathbf{m}_i|X_{1:t},Z_{1:t})
		&=\xi_i P(\mathbf{m}_i|{X_{1:t-1}},Z_{1:t-1})\nonumber\\&\quad\times
		\prod_{l\in\mathcal L_i}
		\hat P(\mathbf{r}_{l,k}|z_{t,l},X_{1:t},Z_{1:t-1}),
		\\
		\hat P(\mathbf{r}_{l,k}|z_{t,l},X_{1:t},Z_{1:t-1})&
		\triangleq \frac{\tilde P(\mathbf{r}_{l,k}|z_{t,l},X_{1:t},Z_{1:t-1})}{P(\mathbf{m}_i|X_{1:t-1},Z_{1:t-1})}
	\end{align*}
	\item Benefit: synergistic update provides a method where all rays are considered simultaneously
	\item Drawback: required assumption that the measurement rays are independent, though they capture the same map
\end{itemize}

@@

\begin{frame}
\frametitle{Probabilistic Occupancy Grid Mapping Conclusions}

@@

@@

\begin{itemize}
	\item Goal: determine robotic actions that maximize map information
	\item Solution: predict future map uncertainty and travel distance to select an optimal pose
\end{itemize}

@@

\begin{frame}
\frametitle{Autonomous Exploration Conclusions}

@@

\section*{}
\subsection*{Multi-Vehicle Coordination}

@@

\begin{itemize}
	\item Multiple agents can accomplish tasks faster and more reliably than a single agent
	\item Large groups are capable of coverage in large environments
	\item Problem: multi-vehicle map information gain optimality can be computationally-intractable
	\item Solution: bidding-based solution simplifies a complicated optimization into a series of simplified optimizations
\end{itemize}

@@

\begin{frame}
\frametitle{Related Work}

@@

\begin{frame}
\frametitle{Proposed Approach}

@@

\begin{frame}
\frametitle{Numerical Example: SEH Second Floor Multi-Vehicle Autonomous Exploration}

@@

\begin{itemize}
	\item Existing Approaches
	\begin{itemize}
		\item Rely on a known map and use Voronoi diagrams to disperse
		\item Another approach introduces cell periodicity: observe long-term dynamics of objects at the same location on the occupancy grid
		\item Bio-inspired approach uses digital pheromones 
		\item Minimizing robot idleness
	\end{itemize}
	\item Proposed Approach
	\begin{itemize}
		\item Degrade occupancy grid cells toward their initial values with exponential decay
		\item Only affects existing probability values without new variables to track
		\item Promotes exploration first, then patrol
	\end{itemize}
\end{itemize}

@@

\begin{frame}
\frametitle{Numerical Example: SEH Second Floor Multi-Vehicle Autonomous Patrol}

@@

\begin{frame}
\frametitle{Multi-Vehicle Autonomous Exploration and Patrol Conclusions}

@@

@@

\begin{enumerate}
	\item Ground vehicle experiment for 2D occupancy grid mapping and autonomous exploration
	\item Flying vehicle experiment in large 3D space resembling an office
	\item Flying vehicle experiment in a complex 3D space
\end{enumerate}
\end{frame}

@@

\begin{frame}
\frametitle{Flying Vehicle in a Large Office-Like Environment}
\begin{itemize}
        	\item Hardware
	\begin{itemize}
		\item NVIDIA Jetson Ubuntu computer-on-module
		\item Asus Xtion IR color depth sensor
		\item Hokuyo LIDAR
		\item VectorNav IMU
	\end{itemize}
	\item Software
	\begin{itemize}
		\item Robot Operating System (ROS)
		\item Vicon Tracker (mocap\_vicon)
		\item Geometric Control: coordinate-free attitude control
	\end{itemize}
\end{itemize}
\begin{figure}
  \centering
  \begin{subfigure}[t]{.4\linewidth}
    \centering\includegraphics[height=.5\linewidth]{quad_top.png}
    \caption*{Quadrotor Top}
  \end{subfigure}
  \begin{subfigure}[t]{.4\linewidth}
    \centering\includegraphics[height=.5\linewidth]{quad_bottom.png}
    \caption*{Quadrotor Bottom}
  \end{subfigure}
\end{figure}
\end{frame}

@@

\begin{frame}
\frametitle{Flying Vehicle in a Complex 3D Environment}
\begin{itemize}
        	\item Full 3D mapping and exploration
	\item Objects are not vertically-uniform
\end{itemize}

@@

\begin{frame}
\frametitle{Full 3D Flying Experiment Video}

@@

\begin{frame}
\frametitle{Experiment Conclusions}
\begin{itemize}
        	\item Experimental environments in 2D and 3D are modeled with occupancy grids
	\item Future entropy prediction and collision-free regions use these occupancy probabilities
	\item A geometric controller is used during flight testing to follow the collision-free trajectory
	\item All algorithms are run in real-time without expensive post-processing 
\end{itemize}
\end{frame}

\section*{}
\subsection*{Conclusions and Publications}

@@

>>>>

\institute{\footnotesize
{\normalsize Evan Kaufman}\\
\vspace*{0.3cm}
Mechanical and Aerospace Engineering\\George Washington University
}

@@

\begin{frame}
\frametitle{Motivation}
\begin{itemize}
	\item Mobile Robotics
	\begin{itemize}
		\item Environments can be dangerous and uncertain
		\item Robots can replace humans for tasks such as surveillance, search-and-rescue, and cleaning
	\end{itemize}
	\pause
	\item Robotic Capabilities
	\begin{itemize}
		\item Robot must understand their environment by generating a map, referred to as \emph{mapping}
		\item Selecting and performing robotic actions to maximize map information, referred to as \emph{autonomous exploration}, is necessary to optimally explore initially-uncertain environments
		\item Cooperative robots can share information to achieve a collective goal with \emph{multi-vehicle exploration and patrol}
		\item These tasks must be performed in 2D and 3D environments, where computational efficiency is paramount to real-time implementation
	\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Research Contributions}
\begin{itemize}
	\item Occupancy Grid Mapping
		\begin{itemize}
		\item Computation of the exact occupancy probability
		\item Incorporation of prior knowledge and new measurements
		\item Bayesian information fusion
	\end{itemize}
	\pause
	\item Autonomous Exploration
	\begin{itemize}
		\item Novel approach to predicting future map uncertainty
		\item Optimal planning to maximize information gain
	\end{itemize}
	\pause
	\item Multi-Vehicle Exploration and Patrol
	\begin{itemize}
		\item Bidding-based framework for assigning tasks while exploring uncertain environments
		\item Map degradation to encourage revisiting regions from the past 
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Outline}
\begin{enumerate}[I]
	\item Occupancy Grid Mapping
	\begin{itemize}
		\item Background and problem definition
		\item Common approaches and approximations
		\item Inverse sensor model in 1D
		\item Ray casting and measurement scans for 2D and 3D environments
		\item Numerical examples
	\end{itemize}
	\pause
	\item Autonomous Exploration
	\begin{itemize}
		\item Existing solutions: frontiers, expected measurements
		\item Proposed approach: entropy expectation
		\item Collision-free trajectories
		\item Optimal pose selection
		\item Numerical examples
	\end{itemize}
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Outline}
\begin{enumerate}[I]
\addtocounter{enumi}{2}
	\item Multi-Vehicle Exploration and Patrol
	\begin{itemize}
		\item Cooperative approaches
		\item Bidding-based framework
		\item Receding horizon
		\item Multi-vehicle autonomous exploration numerical example
		\item Autonomous patrol
		\item Multi-vehicle autonomous patrol numerical example
	\end{itemize}
	\pause
	\item Experiments
	\begin{itemize}
		\item Ground vehicle 2D mapping and autonomous exploration
		\item Aerial quadrotor in large vertically-uniform space
		\item Aerial quadrotor in complex 3D environment
	\end{itemize}
\end{enumerate}
\end{frame}

@@

\begin{frame}
\frametitle{Probabilistic Occupancy Grid Mapping}
\begin{enumerate}[I]
	\item Probabilistic Occupancy Grid Mapping
\end{enumerate}
\end{frame}

@@

\begin{frame}
\frametitle{Approximate Solutions}

@@

\begin{frame}
\frametitle{Proposed Approach: Utilize Invariance}

@@

\begin{itemize}
	\item Unnormalized Probability:
	\begin{align*}
\tilde P(\mathbf{r}_{k}|z,X_{1:t},Z_{1:t-1})
&=\mathbf{P}_k^-
\bigg[\sum_{i=1}^{k-1}\bigg\{\prod_{j=0}^{i-1}\bar{\mathbf{P}}_j^-\bigg\}p(z|\mathbf{r}_{i+},X_t)\mathbf{P}_k^-\bigg]\nonumber\\
&\qquad + \bigg\{\prod_{j=0}^{k-1}\bar{\mathbf{P}}_j^-\bigg\}p(z|\mathbf{r}_{k+},X_t)\mathbf{P}_k^-
\end{align*}
	\item Normalizer:
	\begin{align*}
\label{eqn:allEta}
\eta
&=
\bigg[\sum_{i=1}^{n_{r}+1}\bigg\{\prod_{j=0}^{i-1}\bar{\mathbf{P}}_j^-\bigg\} p(z|\mathbf{r}_{i+},X_t)\mathbf{P}_k^-\bigg]^{-1}
\end{align*}
	\item Solution: $P(\mathbf{r}_{k}|z,X_{1:t},Z_{1:t-1})=\eta\tilde P(\mathbf{r}_{k}|z,X_{1:t},Z_{1:t-1})$
	\item \emph{Linear Complexity}: $\mathcal{O}(n)$ for \emph{all} $n$ cells in FOV compared with $\mathcal O(n\times2^n)$ without using invariance
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Scan Combination Approaches}

\begin{itemize}
	\item \emph{Ray-By-Ray Update}: given a scan of measurement rays, update the map based on each measurement ray \emph{individually} and \emph{sequentially}
	\begin{itemize}
		\item Benefit: the measurement rays maintain some dependency as they capture the same map
		\item Drawback: the best order for evaluating rays is not necessarily chosen
	\end{itemize}
%	\item Conditional probability:
%	\begin{align*}
%		P(\mathbf{m}_i|X_{1:t}&,Z_{1:t})\nonumber\\&
%		=P((\dots(((\mathbf{m}_i|X_{1:t},Z_{1:t-1})|z_{t,1})|z_{t,2})|\ldots)|z_{t,n_z})
%	\end{align*}
	\item \emph{Synergistic Update}: consider every measurement ray inside a scan \emph{simultaneously} to update all grid cells inside the FOV
	\begin{itemize}
		\item Benefit: synergistic update provides a method where all rays are considered simultaneously
		\item Drawback: required assumption that the measurement rays are independent, though they capture the same map
	\end{itemize}
\end{itemize}

@@

\begin{frame}
\frametitle{Probabilistic Occupancy Grid Mapping Summary}

@@

\begin{frame}
\frametitle{Entropy-Based Autonomous Exploration}
\begin{enumerate}[I]
\addtocounter{enumi}{1}
	\item Entropy-Based Autonomous Exploration
\end{enumerate}
\end{frame}

@@

\begin{itemize}
	\item Goal: determine robotic actions that maximize map information
	\item Approach: predict future map uncertainty and travel distance to select an optimal pose
\end{itemize}

@@

\begin{frame}
\frametitle{Autonomous Exploration Summary}

@@

\section*{}
\subsection*{Multi-Vehicle Exploration and Patrol}

\begin{frame}
\frametitle{Multi-Vehicle Exploration and Patrol}
\begin{enumerate}[I]
\addtocounter{enumi}{2}
	\item Multi-Vehicle Exploration and Patrol
\end{enumerate}
\end{frame}

@@

\begin{itemize}
	\item Multi-Vehicle Autonomous Exploration
	\begin{itemize}
		\item Multiple agents can accomplish tasks faster and more reliably than a single agent
		\item Large groups are capable of coverage in large environments
		\item Problem: multi-vehicle map information gain optimality can be computationally-intractable
		\item Approach: bidding-based solution simplifies a complicated optimization into a series of simplified optimizations
	\end{itemize}
	\pause
	\item Multi-Vehicle Autonomous Patrol
	\begin{itemize}
		\item Patrolling large environments with humans is expensive and sometimes dangerous
		\item Several robotic approaches introduce new variables for patrol
		\item Approach: degrade probabilistic occupancy grid over time to encourage revisiting past regions
	\end{itemize}
\end{itemize}

@@

\begin{frame}
\frametitle{Related Work in Multi-Vehicle Exploration}

@@

\begin{frame}
\frametitle{Proposed Approach in Multi-Vehicle Exploration}

@@

\begin{frame}
\frametitle{Numerical Example: SEH Multi-Vehicle Exploration}

@@

\begin{itemize}
	\item Existing Approaches
	\begin{itemize}
		\item Rely on a known map and use Voronoi diagrams to disperse
		\item Another approach introduces cell periodicity: observe long-term dynamics of objects at the same location on the occupancy grid
		\item Bio-inspired approach uses digital pheromones 
		\item Minimizing robot idleness
	\end{itemize}
	\pause
	\item Proposed Approach
	\begin{itemize}
		\item Degrade occupancy grid cells toward their initial values with exponential decay
		\item Only affects existing probability values without new variables to track
		\item Promotes exploration first, then patrol
	\end{itemize}
\end{itemize}

@@

\begin{frame}
\frametitle{Numerical Example: SEH Multi-Vehicle Patrol}

@@

\begin{frame}
\frametitle{Multi-Vehicle Exploration and Patrol Summary}

@@

\begin{frame}
\frametitle{Experiments}
\begin{enumerate}[I]
\addtocounter{enumi}{3}
	\item Experiments
\end{enumerate}
\end{frame}

@@

\begin{enumerate}
	\item Ground vehicle experiment for 2D occupancy grid mapping and autonomous exploration
	\item Aerial vehicle experiment in large 3D space resembling an office
	\item Aerial vehicle experiment in a complex 3D space
\end{enumerate}
\end{frame}

@@

\begin{frame}
\frametitle{Aerial Vehicle in a Large Office-Like Environment}
\begin{itemize}
        	\item Hardware
	\begin{itemize}
		\item NVIDIA Jetson Ubuntu computer-on-module
		\item Asus Xtion IR color depth sensor
		\item Hokuyo LIDAR
		\item VectorNav IMU
	\end{itemize}
	\item Software
	\begin{itemize}
		\item Robot Operating System (ROS)
		\item Vicon Tracker (mocap\_vicon)
		\item Geometric Control: coordinate-free attitude control
	\end{itemize}
\end{itemize}
\begin{figure}
  \centering
  \begin{subfigure}[t]{.4\linewidth}
    \centering\includegraphics[height=.5\linewidth]{quad_top.png}
    \caption*{Quadrotor Top}
  \end{subfigure}
  \begin{subfigure}[t]{.4\linewidth}
    \centering\includegraphics[height=.5\linewidth]{quad_bottom.png}
    \caption*{Quadrotor Bottom}
  \end{subfigure}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Aerial Vehicle in a Large Office-Like Environment}
\begin{itemize}
        	\item Environment Size: $10.8$ m $\times$ $11.8$ m $\times$ $1.65$ m
\end{itemize}
\begin{figure}
  \centering
  \begin{subfigure}[t]{.4\linewidth}
    \centering\includegraphics[width=\linewidth]{experiment_north.jpg}
    \caption*{North Region}
  \end{subfigure}
  \begin{subfigure}[t]{.4\linewidth}
    \centering\includegraphics[width=\linewidth]{experiment_south.jpg}
    \caption*{South Region}
  \end{subfigure}
\end{figure}
\end{frame}

@@

\begin{frame}
\frametitle{Aerial Vehicle in a Complex 3D Environment}
\begin{itemize}
        	\item Full 3D mapping and exploration
	\item Objects are not vertically-uniform
	\item Environment Size: $9.0$ m $\times$ $8.5$ m $\times$ $2.25$ m
\end{itemize}

@@

\begin{frame}
\frametitle{Full 3D Aerial Experiment Video}

@@

\begin{frame}
\frametitle{Experiment Summary}
\begin{itemize}
        	\item Experimental environments in 2D and 3D are modeled with occupancy grids
	\item Future entropy prediction and collision-free regions use these occupancy probabilities
	\item A geometric controller is used during flight testing to follow the collision-free trajectory
	\item All algorithms are run in real-time without expensive post-processing 
\end{itemize}
\end{frame}

\section*{}
\subsection*{Conclusions}

@@

\begin{frame}
\frametitle{Thanks}
\begin{itemize}
        	\item Special thanks to the US Naval Research Lab for support under project ``Intelligent Microflyer''
	\item Questions
\end{itemize}
\end{frame}
